### 2022-11-11 NSF2022/Description/specificaim2.tex
cleaned up BIE section a bit

>>>>

To briefly describe IE formulations of PDEs, we consider the Stokes
equation~\eqref{eqn:stokes} as an example. Its solution can be written
as a convolution 
\begin{align*}
  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
\end{align*}
where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
is an unknown density function. The IE reformulation has several
immediate advantages including a dimension reduction since $\ssigma$ is
defined only on $\partial \Omega(t)$, and the far field boundary
condition of the PDE is automatically satisfied. The density
function $\ssigma$ is chosen to satisfy the boundary condition, and this
results in a IE 
\begin{align*}
  \gg(\xx) = \lambda \ssigma(\xx) + 
    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
    \quad \xx \in \partial\Omega(t),
\end{align*}
where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
constant that depends on the choice of $G$. For numerical stability,
choices of $G$ that result in second-kind Fredholm integral equations,
meaning $\lambda \neq 0$, are preferred.
